Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
Shorten methods

% intro
We used three subdatasets of the publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
used by other research groups for independent research questions
(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% AD & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).
% procedure: questionnaire
Subjects filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AD & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy the
audiobook'' or ``enjoy the movie'' respectively.
% AD & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

\todo[inline]{contrary to claims in Sengupta, the pictures are NOT the same
as used in Haxby, 2011; sets might have an intersection though}

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% mirror images
Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% paradigm implementation
In all three studies, stimulation was implemented with
\href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a
computer with the NeuroDebian operating system \citep{halchenko2012open}.

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer.
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$\times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

\todo[inline]{auditory stimulation was the same in AD and AV?}

% AD & AV: auditory stimulation
In the AD and AV study, auditory stimulation was delivered through an MR confon
mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
sound card through an optical connection.

@@

\todo[inline]{shorten this subsection a lot}

% AD
In the AD study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
volumes for segment 1–8).

>>>>

% intro
We used three components of the publicly available
\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already been
used by other research groups in independent studies
(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the original movie (AV study;
\citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% AD & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes, less relevant to the main plot, were removed to create
the ``research cut'' lasting \unit[$\approx$2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning.
% splitting
Each stimulus was split into eight segments of approximately \unit[15]{minutes}.
% AD & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy''.
% AD & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore. During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.
% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen
% screen size
at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
\unit[23.75 $\times$ 10.25]{cm}.\todo{replace with visual angle size, in line with VIS}
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

% AD & AV: auditory stimulation
Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
headphones (AV), which reduced the scanner noise by
at least \unit[20–30]{dB}.

@@

Gradient-echo fMRI data for the AD study were acquired using a \unit[7]{Tesla}
Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
receive coil at \unit[2]{s} repetition time (TR) with 36 axial slices (thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view, anterior-to-posterior phase encoding direction) and a
\unit[10]{\%} inter-slice gap, recorded in ascending order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions.

% AV & VIS
In the AV and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
at \unit[2]{s} repetition time with
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction, recorded in ascending order.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (AD and AV).
